%-------------------------
% Resume in Latex
% Author : Samim Taray
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{parskip}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
% \addtolength{\oddsidemargin}{-0.5in}
% \addtolength{\evensidemargin}{-0.5in}
% \addtolength{\textwidth}{1in}
\addtolength{\topmargin}{2.2cm}
\addtolength{\textheight}{2.4cm}

\urlstyle{same}

\setlength{\tabcolsep}{0cm}
\setlength{\parindent}{0pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

\begin{document}

\textbf{Dear Snowflake Team,}
\vspace{1cm}


I am writing this letter in support of my application for the Software Engineer
position at your Berlin office. I am excited to apply to this position for multiple reasons. Firstly, I
find this is to be a unique opportunity to contribute to the development of
new cloud based data processing products that have a high impact and reach a
large number of customers.
Secondly, I find it very exciting to work on large scale distributed systems
and solve problems related to availability, reliability and performance.
I also see this as a unique opportunity to further develop skills in the general
area of software development by collaborating with experts at Snowflake.
I firmly believe that I possess the qualifications, skills and the drive to
excel in this position and be a valuable member of the engineering team at
Snowflake.

Currently I am a full-time Software Engineer at K-Lens GmbH. in Saarbr\"ucken,
Germany where I work on designing, implementing and
optimizing scientific algorithms for computer vision applications. Our products
are still in early development but we have shipped software to some industrial
customers which include big automotive parts manufacturers. I also work on
development of algorithms and applications for our consumer focussed
product where I am involved in designing and integrating new algorithms and features
into our existing codebase in C++ and writing applications, internal tools and
automated tests used for alpha and internal testing most often using C++
or Python. Prior to this, I was a Master student at Saarland University. I did my master thesis in
collaboration with K-Lens GmbH. after which I was offered the opportunity to
work here full time. I possess a solid foundation in the principles and
internal workings of Operating Systems, Distributed Systems and concurrent programs through graduate
level course work and projects. For example in Operating Systems
course, I coded major parts of an OS including user program support, a virtual
memory subsystem and an indexed file system. I have experience in developing
distributed systems from a course project where I had to code a distributed
file service in C++. I believe my experience demonstrates that I possess the
necessary skills needed to be efficient and successful in this role.

I possess good written and verbal communication skills in English. I can convey
my thoughts and ideas clearly and I always try to follow an approach based on
understanding and reasoning to any problem. I love to learn new things.
I push myself to keep improving in the areas of software design,
software best practices and problems solving. I love to dig deeper into any
problem or technology I work with. Because of these qualities, I think I can
quickly learn the things needed to be efficient and successful in this role.

As a person I think I am easy to work with. I enjoy collaboration and knowledge
sharing. At the same time, I am not afraid to develop my own ideas and work
independently.

I hope I have convinced you of my passion for this work. I look forward to
hearing from you.

\vspace{1cm}
\textbf{Sincerely}

Samim Zahoor Taray

\end{document}

%% end of file `template.tex'.
